---
title: "DATA471 Assignment 5"
author: "kakauchad_300212228"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(ggplot2)
library(ggfortify)
library(dplyr)
```
# Assignment info

  1. Read in data  
  2. Initial Data Analysis  
  3. Preprocess data  
  4. carry out tasks  
  5. Answer the questions  
  
## Read in the data  
The data comprises 11 csv files providing weather and climate information for three locations in the Hong Kong region:  Wong Chuk Hang (HKS), Tseung Kwan O (JKB), King's Park (KP).  Each location has a file for each of: 'Rainfall (mm)' (RF), 'Wind Speed (km/h/)' (WSPD), 'Maximum Temperature (degrees Celsius)' (CLMMAXT), 'Minimum Temperature (degrees Celsius)' (CLMMINT), 'Mean Temperature (degrees Celsius)' (CLMTEMP).


```{r readInData}
# read in weather data from three regions in HK
# collect names of data files
csv_files <- list.files("./DATA471_A5_datasets")
path <- './DATA471_A5_datasets'
hks_max <- read.csv(paste(path,'CLMMAXT_HKS.csv', sep = '/'), skip = 2, header = T, )
hks_col  <- read.csv(paste(path,'CLMMAXT_HKS.csv', sep = '/'), skip = 2, header = F, nrows = 1 )
hks_col <- iconv(hks_col, "latin1", "ASCII", sub = "")


for (i in 1:2) {
  
}
```

